\section{OpenNMS Community}
The \emph{OpenNMS} community is a global community consisting of developers, corporations, service providers, researchers and users.

\subsection*{Role of the OpenNMS Group}
One of the biggest part of code and project contribution is made by \emph{The OpenNMS Group, Inc.} The \emph{OpenNMS Group} build a business and builds a bridge to get the software \emph{OpenNMS} as 100\% free software into commercial companies and help with development and support. The \emph{OpenNMS Group} is providing people a place for people willing to be a full time contributor and a main driver for the OpenNMS project. They provide a place to build the infrastructure to deploy and manage the project with the following parts:
\begin{itemize}
  \item Public continous integration system to build, test, compile and deploy OpenNMS 
  \item Packaging and providing infrastructure distributing pre-compiled packages for different operating systems and \emph{Linux/Unix} distributions
  \item Public issue tracking for bugs, enhancements and feature requests
  \item Providing and running public mailing lists
  \item Maintaining the software branches and source code repository on \emph{github}
  \item Software release management
\end{itemize}

\subsection*{OpenNMS Foundation Europe}
To cover non-commercial interests the \emph{OpenNMS Foundation Europe e.V.} (OFE) was founded in July 31st. in Fulda, Germany. It is a registered non-profit organization. The objective of the organization is to promote the use and development of free open source software, especially \emph{OpenNMS} the research and education around free open source software and network (management) technologies. To do this, the \emph{OFE} organizes conferences and trainings and acts as an advocate for free open source software. The \emph{OFE} initiates software development and studies which are made available to the public under the \emph{GPL}\footnote{GNU General Public License: \url{http://www.gnu.org/licenses/gpl.html}} or a suitable successor.

\subsection*{Your Contribution to OpenNMS}
If you are a developer that would like to contribute to OpenNMS you will need to sign the \emph{OpenNMS Contributor Agreement}. You can find agreement at the following link \url{http://www.opennms.org/wiki/Contributor_Agreement}.
\begin{itemize}
  \item \url{http://www.opennms.org/wiki/Developing_with_Git}
  \item \url{http://www.opennms.org/wiki/Eclipse_and_OpenNMS}
\end{itemize}

\subsection*{Issue tracking system and build system}
To document bugs, enhancements and feature request, the \emph{OpenNMS Group, Inc.} provide and maintains a public \emph{Atlassian JIRA} installation. It is recommended you create your JIRA account, which allows you to document bugs, enhancements or feature requests. The application for issue and feature tracking is available on \url{http://http://issues.opennms.org}.

The OpenNMS software development follows a test driven approach. To provide a stable and continous quality of the code base, the \emph{OpenNMS Group} provides and run \emph{Atlassian Bamboo} as a build system. It compiles, tests and deploys the OpenNMS software from the public \emph{git} repositories.