\section{Community Support Tools}



\subsection*{Issue tracking, code browser and build system}
To document bugs, enhancements and feature request, the \emph{OpenNMS Group, Inc.} provide and maintains a public \emph{Atlassian JIRA} installation. It is recommended you create your JIRA account, which allows you to document bugs, enhancements or feature requests. The application for issue and feature tracking is available on \url{http://issues.opennms.org}.

The \emph{OpenNMS} software development follows a test driven approach. To provide a stable and continous quality of the code base, the \emph{OpenNMS Group} provides and run \emph{Atlassian Bamboo} as a build system. It compiles, tests and deploys the \emph{OpenNMS} software from the public \emph{git} repositories. The build system is public available on \url{http://bamboo.internal.opennms.com:8085}.

\emph{The OpenNMS Group} provides public access to \emph{Atlassian Fisheye} which gives the possibility to browse code from a browser and search for commit messages. The code browser is available on \url{http://fisheye.opennms.org}.

\begin{itemize}
  \item Continous integration to build, test, compile and deploy OpenNMS.
  \item Packaging and providing infrastructure distributing pre-compiled packages for different operating systems and \emph{Linux/Unix} distributions
  \item Issue tracking for bugs, enhancements and feature requests
  \item Providing and running mailing lists
  \item Maintaining the software branches and source code repository
  \item Organizing and plan the software release management
\end{itemize}